A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2019-02-19 reviewer_response.tex

{\color{blue}{2) Among the various existing models used in this work, some explicitly report the use of LJ long range corrections in the energy and pressure. The authors should clearly state if they have taken that into account in their simulations.}}

\textbf{Answer}: The reviewer is right. We applied standard tail corrections to the LJ interactions for all systems under investigation. This information was included on page 5 of the manuscript.

{\color{blue}{3) Results on densities of the various IL models at 298 K (Table 1) differ from the ones reported in the initial references. For example,  an 1\% error is presented in this manuscript for the FF-3 model of Koller \textit{et al.}, while an excellent agreement with the experimental density is reported in the original paper of Koller and his co-workers. The authors should explain this discrepancy.}}

\textbf{Answer}: The differences in density between our results and those reported by Koller \textit{et al}. \cite{Koller_2012}, Batista \textit{et al}. \cite{Batista_2015}, Liu \textit{et al}. \cite{Liu_2014}, and Weber and Kirchner \cite{Weber_2016} are, respectively, 1.0\% , 6.2\%, 1.8\%, and 0.5\%.
With the exception of the force field introduced by Batista \textit{et al}. \cite{Batista_2015}, the discrepancies are small.
In all cases, we tried to carefully follow the simulation setup reported by those authors, except for the number of ion pairs.
For instance, Koller and co-workers \cite{Koller_2012} simulated 58 ions pairs, while we considered 250 ion pairs.
Small differences are then expected.
The discrepancy with the results of Batista and co-workers \cite{Batista_2015} stands out from the others.
In this case, however, important computational details are missing in the original paper, such as the method for computing electrostatic interactions, as well as the factors for scaling the 1-4 non-bonded interactions. 
Considering these various factors, we did not focus on reproducing the results of these references, but rather on using the force field parameters reported therein and find those parameter sets that best reproduce the experimental Henry's law constants of \ce{CO_2}.

### 2019-02-19 ionic_liquids.tex
Resubmitted version

With the aim of setting up a computationally efficient protocol for the IL simulations, in this work we assess the possibilities of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing electrostatic interactions.
In this method, the electrostatic potential between two atoms with charges $q_i$ and $q_j$ interacting at a distance $r$ is given by
\begin{equation}
V_\text{DSF}(r) = V(r) - V(r_c) - V^\prime(r_c)(r-r_c),
\end{equation}
where $V(r) = q_i q_j {\text{erfc}(\alpha r)}/{r}$ is a damped Coulomb potential.
This potential is cut off at $r = r_c$, which makes it short-ranged and thus a cheaper alternative to Ewald-type schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}.
McCann \textit{et al}. \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force field.
They concluded that using $\alpha = 0.2~\text{\AA}^{-1}$ and $r_c = 15~\text{\AA}$ provides the best energetic agreement with the Ewald method.
In this work, detailed comparisons are made in terms of the simulated densities and radial distribution functions.
In Sec.~\ref{sec:results}, we show that by using the same $\alpha$ value but a considerably smaller cutoff distance ($r_c = 12 \text{\AA}$) one can obtain suitable results.
These values were employed here for the ILs as well as for solutes containing partially charged atoms.
The only exception was hexane, for which the use of undamped Coulombic interactions (i.e. $\alpha = 0$) resulted in improved chemical potential predictions. That cutoff distance was also used for truncating the LJ interactions, for which we applied analytical tail corrections \cite{allen}. In addition, we used the Lorentz-Berthelot mixing rules to calculate the cross LJ interactions, except for the solutes modeled with the OPLS-AA force fields, which employs geometric combining rules.

@@

In order to obtain minimum-energy conformations, we first carried out MD simulations of isolated ion pairs.
For this, we used a Nos\'{e}-Hoover chain thermostat \cite{Martyna1992} with set-point temperature gradually changing down to nearly $0~\text{K}$.
The resulting coordinates were then used with the PACKMOL algorithm \cite{Mart_nez_2009} via the Playmol package \cite{playmol} to obtain initial liquid-phase configurations.
The expanded ensemble procedure, the softcore potential, and the DSF method  with linear coupling were implemented by customizing the LAMMPS package \cite{Plimpton1995}, which we used for carrying out all the simulations in this work.

>>>>

With the aim of setting up a computationally efficient protocol for the IL simulations, in this work we assess the possibilities of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing electrostatic interactions.
In this method, the electrostatic potential between two atoms with charges $q_i$ and $q_j$ interacting at a distance $r$ is given by
\begin{equation}
V_\text{DSF}(r) = V(r) - V(r_c) - V^\prime(r_c)(r-r_c),
\end{equation}
where $V(r) = q_i q_j {\text{erfc}(\alpha r)}/{r}$ is a damped Coulomb potential.
This potential is cut off at $r = r_c$, which makes it short-ranged and thus a cheaper alternative to Ewald-type schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}.
McCann \textit{et al}. \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force field.
They concluded that using $\alpha = 0.2~\text{\AA}^{-1}$ and $r_c = 15~\text{\AA}$ provides the best energetic agreement with the Ewald method.
In this work, detailed comparisons are made in terms of the simulated densities and radial distribution functions.
In Sec.~\ref{sec:results}, we show that by using the same $\alpha$ value but a considerably smaller cutoff distance ($r_c = 12 \text{\AA}$) one can obtain suitable results.
These values were employed here for the ILs as well as for solutes containing partially charged atoms.
The only exception was hexane, for which the use of undamped Coulombic interactions (i.e. $\alpha = 0$) resulted in improved chemical potential predictions. The same cutoff distance was used for truncating the LJ interactions, for which we applied analytical tail corrections \cite{allen}. In addition, we used the Lorentz-Berthelot mixing rule to calculate the LJ interactions of unlike atoms, except for the solutes modeled with the OPLS-AA force fields, in which geometric combining rules are employed.

@@

In order to obtain minimum-energy conformations, we started by carrying out MD simulations of isolated ion pairs.
For this, we used a Nos\'{e}-Hoover chain thermostat \cite{Martyna1992} with set-point temperature gradually changing down to nearly $0~\text{K}$.
The resulting coordinates were then used with the PACKMOL algorithm \cite{Mart_nez_2009} via the Playmol package \cite{playmol} to obtain initial liquid-phase configurations.
The expanded ensemble procedure, the softcore potential, and the DSF method  with linear coupling were implemented by customizing the LAMMPS package \cite{Plimpton1995}, which we used for carrying out all the simulations in this work.
